\documentclass{article}

\begin{document}
\paragraph{Title: } Submerged Echoes

\paragraph{Genre: } Thrust-like, Puzzle, Mystery

\paragraph{Visual style: } Geometric/Low Poly

\paragraph{Short Description: } A batyscaphe has to investigate the sinking of a submarine

\paragraph{Setting: } The game is set in the deep of the ocean

\paragraph{Main Characters: } The main character is the pilot of the bathyscaphe

\paragraph{Synopsis: } The story is about the pilot of a bathyscaphe who is sent investigating the
sinking of a submarine in the deep of the ocean.
Soon the pilot finds the submarine who crushed in a cave without explanations, thus he set off to find
the black box.
He descends into a tunnel in which he, mysteriously, finds the black box along with a strange statue.
Returning back he notices that a new tunnel has appeared: he can then chose if going down this mysterious new tunnel or returning back to surface.
Descending in the newfound tunnel he hears strange voices and distant calls and finally finds himself in a room with an enormous statue, with three empty sockets in place of the eyes.
The pilot then explores the nearby tunnels, overcoming difficulties and traps, in order to retrieve the orbs and place them back again in the statue.
When the pilot places all the orbs in the sockets a earthquake starts and he is filled with dreadful images and horrific scenes... Then the game ends.
\paragraph{Rules and Mechanics: } 
\begin{itemize}
\item The main goal of the game is to complete the main story, completing all the levels;
\item The control system is inspired by Thrust and similar games: 
	\begin{itemize}
	\item With two keys (Q/E) the player can control the rotation of the bathyscaphe;
	\item With another key (Space) the player can apply thrust and thus move the bathyscaphe forward.
	\end{itemize}
\item When the bathyscaphe hits a wall or other obstacles it explodes and the game restarts from the first level;
\item In some levels the player is able to choose between alternative actions.
\end{itemize}

\paragraph{Requirements: } \begin{itemize}
\item Low-poly geometric model of the bathyscaphe;
\item Low-poly geometric model of the submarine;
\item Low-poly geometric model of the statue;
\item Low-poly geometric scenes/levels
\end{itemize}


\section{Sequences}
\subsection{Sequence 1 (Initial Descending)}

\paragraph{Description: } The player descends into a tunnel, in order to find the sunken submarine.
\paragraph{Narrative: } 
\begin{itemize}
\item We lost contact with the Queen Mary for three days straight
\item The command sent a fleet of three to investigate
\item I was the third
\end{itemize}
[When enters tunnel]
\begin{itemize}
\item As i descended into the tunnel I lost every signal
\item I was alone
\end{itemize}
\paragraph{Next levels: } Sequence 2
\paragraph{Objects: } -

\subsection{Sequence 2 (Finding the Queen Mary)}

\paragraph{Description: } The player finds the sunken submarine and has to find the black box.
\paragraph{Narrative: } 
\begin{itemize}
\item And there it was, sunken, irremediably lost...
\item A badly conducted maneuvre? A problem with the navigation system?
\item Only the black box could give us the answers...
\item But there were no signs of it...
\end{itemize}
\paragraph{Next levels: } Sequence 3
\paragraph{Objects: } -

\subsection{Sequence 3 (Finding the Black Box)}

\paragraph{Description: } The player finds the black box in a nearby tunnel.
\paragraph{Narrative: } 
\begin{itemize}
\item Strange place for a black box, wasn't it?
\item How it managed to end in that tunnel?
\end{itemize}
\paragraph{Next levels: } Sequence 4
\paragraph{Objects: } Black box

\subsection{Sequence 4 (Back to Queen Mary)}

\paragraph{Description: } The player returns back with the black box and notices a new tunnel
\paragraph{Narrative: } 
\begin{itemize}
\item I recovered the black box... My mission was complete...
\item However, as I prepared to re-emerge, I noticed something...
\item A tunnel? Was it there before?
\item Something buried deep within me urged me to enter it...
\end{itemize}
\paragraph{Next levels: } 
\begin{itemize}
\item Sequence 5a (go back)
\item Sequence 5b (go through the new tunnel)
\end{itemize}
\paragraph{Objects: } -

\subsection{Sequence 5a (Good Ending)}

\paragraph{Description: } The player reemerges with the black box
\paragraph{Narrative: } 
\begin{itemize}
\item Fighting against myself I managed to return back, carrying the black box with me...
\item Finally we would have the answers we sought...
\end{itemize}
\paragraph{Next levels: } -
\paragraph{Objects: } -



\subsection{Sequence 5b (Descending the tunnel)}

\paragraph{Description: } The player descends the newlyfound tunnel
\paragraph{Narrative: } 
\begin{itemize}
\item Descending the tunnel I heard them...
\item Feeble voices... Primal screams... Calling in my head
\item Whispering horrors in long forgotten languages...
\item Yet so deeply familiar
\end{itemize}
\paragraph{Next levels: } Sequence 6
\paragraph{Objects: } -

\subsection{Sequence 6 (Statue's room)}

\paragraph{Description: } The player enters a room with a giant statue
\paragraph{Narrative: } 
[When near statue]
\begin{itemize}
\item Finally I reached a new, enormous room...
\item In the middle of it stood a huge statue...
\item I cannot explain what it depicted... Something so alien, so utterly wrong...
\item Three empty socket were in place of the statue's eyes...
\end{itemize}
[When Challenge orb taken]
\begin{itemize}
\item A floating sphere stood in front of the statue...
\item When i took it I heard a sound like a distant click.
\end{itemize}
\paragraph{Next levels: }
\begin{itemize}
\item Sequence 7a
\item Sequence 7b
\item Sequence 7c
\end{itemize}
\paragraph{Objects: } Challenge orb

\subsection{Sequence 7a (First Challenge)}

\paragraph{Description: } Room with a path through static obstacles
\paragraph{Narrative: } -
\paragraph{Next levels: } Sequence 8
\paragraph{Objects: } First orb

\subsection{Sequence 7b (Second Challenge)}

\paragraph{Description: } Room with a path through a series of sliding obstacles
\paragraph{Narrative: } -
\paragraph{Next levels: } Sequence 8
\paragraph{Objects: } Second orb

\subsection{Sequence 7a (Third Challenge)}

\paragraph{Description: } Room with a path through two series of timed sliding obstacles
\paragraph{Narrative: } -
\paragraph{Next levels: } Sequence 8
\paragraph{Objects: } Third orb

\subsection{Sequence 8 (Bad ending)}

\paragraph{Description: } Same room as Sequence 6, but with ending interaction
\paragraph{Narrative: }
[When all three orbs collected]
\begin{itemize}
\item As I placed all three orbs in the empty sockets the cave began to shake violently...
\item It seemed as the world was breaking apart...
\item Suddenly my mind was filled with horrorific vivid images...
\item I saw orrendous dead creatures, similar in shape to the statue, rising from their iced graves...
\item I saw sacrifices and blasphemous rituals made in name of gods whose names were long forgotten...
\item I saw distant dying stars, slowly consumed by entropy...
\item And then... Nothing...
\end{itemize}
\paragraph{Next levels: } -
\paragraph{Objects: } -

\end{document}